---
title: "Geocoder API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geocoder API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(hereR)
library(mapview)
addresses <- poi$city
geocoded <- hereR:::example$geocode
```

Geocode addresses using the 'HERE Geocoder' API.

## Geocode addresses
In order to geocode addresses, the function `geocode` is used. The requests are sent asynchronously, which means that every geocoded address is counting as one request. The addresses have to be of type `character`:

```{r print_addresses, eval=TRUE, echo=TRUE, out.width='100%'}
head(addresses, 3)
```

Geocode the character vector containing the addresses:
```{r geocode, eval=FALSE}
geocoded <- geocode(addresses)
```

The return value is an `sf` object containing `POINT` geometries of the addresses:
```{r head_geocoded, eval=TRUE, echo=TRUE, out.width='100%'}
head(geocoded, 3)
```

Print the geocoded addresses on an interactive leaflet map:
```{r map_geocoded, eval=TRUE, out.width='100%'}
mapview(geocoded,
        label = geocoded$address,
        col.regions = "yellow",
        map.types = c("Esri.WorldTopoMap"),
        legend = FALSE,
        homebutton = FALSE
)
```

## API Reference

* [Geocoder](https://developer.here.com/documentation/geocoder/topics/resource-geocode.html)
