---
title: "Geocoder API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geocoder API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(hereR)
library(data.table)
library(mapview)
addresses <- poi$city
geocoded <- hereR:::example$geocode
suggestions <- hereR:::example$autocomplete
rev_addresses <- hereR:::example$reverse_geocode_addresses
rev_landmarks <- hereR:::example$reverse_geocode_landmarks
```

Geocode addresses using the 'HERE Geocoder' and 'HERE Geocoder Autocomplete' APIs.

## Geocode addresses
In order to geocode addresses, the function `geocode()` is used. The requests are sent asynchronously, which means that every geocoded address is counting as one request. If the option `autocomplete` is set to `TRUE`, the addresses are sent to the 'Geocoder Autocomplete' API before geocoding, which improves matches but doubles the amount of requests. The addresses have to be of type `character`:

```{r print_addresses, eval=TRUE, echo=TRUE, out.width='100%'}
head(addresses, 3)
```

Geocode the character vector containing the addresses:
```{r geocode, eval=FALSE}
geocoded <- geocode(addresses, autocomplete = FALSE)
```

The return value is an `sf` object containing `POINT` geometries of the addresses:
```{r head_geocoded, eval=TRUE, echo=TRUE, out.width='100%'}
head(geocoded, 3)
```

Not found addresses are deleted from the result. This means that the sf object may contain fewer rows than the original number of addresses. However, the row names of the returned `sf` object are still matching the index of the geocoded addresses. Using the row names a corresponding `data.frame` `"df"` could be added to the geocoded addresses.
```{r join_geocoded, eval=FALSE, echo=TRUE, out.width='100%'}
geocoded_sfdf <- st_as_sf(data.frame(geocoded, df[row.names(geocoded), ]))
```

Print the geocoded addresses on an interactive leaflet map:
```{r map_geocoded, eval=TRUE, out.width='100%'}
mapview(geocoded,
        label = geocoded$address,
        col.regions = "yellow",
        map.types = c("Esri.WorldTopoMap"),
        legend = FALSE,
        homebutton = FALSE
)
```

## Autocomplete addresses

The Geocoder Autocomplete API can be accessed using the `autocomplete()` function. The `results` parameter defines the maximum number of suggestions that should be requested for each address.
```{r autocomplete, eval=FALSE}
suggestions <- autocomplete(addresses, results = 3)
```

The return value is a `data.table` containing autocomplete suggestions for the addresses. The variable `id` matches the index of the initial address vector, which was used as input and `order` stores the rank of the suggestion.

```{r results_autocomplete, eval=TRUE, echo=TRUE, out.width='100%'}
results <- data.table(
  input = addresses[suggestions$id],
  rank = suggestions$order,
  suggestion = suggestions$label
)
```

```{r table_results, eval=TRUE, echo=FALSE, out.width='100%', fig.align='center'}
knitr::kable(head(results), format = "html")
```

## Reverse geocode POIs
The reverse geocoding feature of the Geocoder API can be accessed using the `reverse_geocode()` function. The function allows to retrieve addresses (`landmarks = FALSE`) or landmarks (`landmarks = TRUE`) near POIs. 

```{r reverse_geocode, eval=FALSE, echo=TRUE, out.width='100%'}
rev_addresses <- reverse_geocode(poi = poi, results = 3, landmarks = FALSE)
rev_landmarks <- reverse_geocode(poi = poi, results = 3, landmarks = TRUE)
```

The function returns an `sf` object, containing the suggested addresses or landmark names of the reverse geocoded POIs. The coordinates are different from the initially provided POIs since they represent the locations of the suggested addresses or landmarks.

```{r map_reverse_geocode, eval=TRUE, echo=TRUE, out.width='100%'}
m <-
  mapview(poi, alpha.region = 0, col.region = "transparent",
          label = poi$city, cex = 30, layer.name = "POIs",
          map.types = c("Esri.WorldTopoMap"), homebutton = FALSE) +
  mapview(rev_addresses, col.region = "yellow", alpha = 0,
          label = rev_addresses$label, layer.name = "Adresses",
          homebutton = FALSE) +
  mapview(rev_landmarks, col.region = "red", alpha = 0,
          label = rev_landmarks$name, layer.name = "Landmarks",
          homebutton = FALSE)
m
```

If no addresses or landmarks are found near a POI, `NULL` for this POI is returned. In this case the rows corresponding to this particular POI are missing and merging the POIs by row is not possible. However, in the returned `sf` object, the column `"id"` matches the rows of the input POIs. The `"id"` column can be used to join the original POIs.

## API Reference

* [Autocomplete](https://developer.here.com/documentation/geocoder-autocomplete/dev_guide/topics/resource-suggest.html)
* [Geocoder](https://developer.here.com/documentation/geocoder/topics/resource-geocode.html)
* [Reverse Geocoder](https://developer.here.com/documentation/geocoder/dev_guide/topics/resource-reverse-geocode.html)
